Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-01-30 PAPER.tex
Massage case study language a tad.

We now present a case study of these same three themes using data from the PAPER experiment. We use the intuition 
developed through the toy model simulations in order to make a new analysis of the PAPER-64 dataset originally presented in 
A15 and obtain a revised power spectrum estimate.

>>>>

We now apply these lessons to data from the PAPER experiment to make a new analysis of the PAPER-64 dataset originally presented in 
A15 and obtain a revised power spectrum estimate.
